\pkg{cleanR}: Maid for Cleaning Datasets in \proglang{R}

### 2016-10-18 latex/article.Rnw

\documentclass[article]{jss}
\usepackage[utf8]{inputenc}
\usepackage[nogin]{Sweave}
\usepackage{pdfpages}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}

@@

\newcommand{\hl}[1]{\textcolor{magenta}{#1}}
\newcommand{\R}{\proglang{R}}

@@

%% almost as usual
\author{Claus Thorn Ekstr\o m\\Biostatistics\\Department of Public
  Health\\University of Copenhagen \And
        Anne Helby Petersen\\Biostatistics\\Department of Public
  Health\\University of Copenhagen}
\title{\pkg{cleanR}: Your Personal Maid for Cleaning Datasets in \proglang{R}}

%% for pretty printing and a nice hypersummary also set:
\Plainauthor{Claus Thorn Ekstr\o m, Anne Helby Petersen} %% comma-separated
\Plaintitle{{cleanR}: Your maid for cleaning datasets in R} %% without formatting
\Shorttitle{\pkg{cleanR}: maid for cleaning datasets in R} %% a short title (if necessary)

@@

%% The address of (at least) one author should be given
%% in the following format:
\Address{
  Claus Thorn Ekstr\o m\\
  Biostatistics, Department of Public Health\\
  University of Copenhagen\\
  Denmark\\
  E-mail: \email{ekstrom@sund.ku.dk}\\
  URL: \url{http://eeecon.uibk.ac.at/~zeileis/}
}
%% It is also possible to add a telephone and fax number
%% before the e-mail in the following format:
%% Telephone: +43/512/507-7103
%% Fax: +43/512/507-2851

@@

The manusccript is organized as follows. Section \ref{sec:example1}
presents a worked example and tutorial on how to use the \pkg{cleanR}
package to create a summary of potential errors. Section
\ref{sec:internals} illustrates the methodology of modeling
proportional data using simplex generalized regression. The
generalized estimating equations for longitudinal proportional
outcomes are given in Section 4. Then we address model diagnostics in
Section 5. Section 6 presents the details of the simplexreg
package. Section 7 further conducts analyses based on the simplex
distribution in R with real data sets. Finally, plans for extending
the package are described in Section 8.

@@

In \pkg{cleanR} the clean function is the primary workhorse and it
should be an ideal starting place

>>>>

\documentclass[article]{jss}
\usepackage[utf8]{inputenc}
\usepackage[nogin]{Sweave}
\usepackage{pdfpages}
\usepackage{xspace}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}

@@

\newcommand{\hl}[1]{\textcolor{magenta}{#1}}
\newcommand{\R}{\proglang{R}\xspace}

@@

%% almost as usual
\author{Anne Helby Petersen\\Biostatistics\\Department of Public
  Health\\University of Copenhagen \And Claus Thorn Ekstr\o m\\Biostatistics\\Department of Public
  Health\\University of Copenhagen}
\title{\pkg{cleanR}: Maid for Cleaning Datasets in \proglang{R}}

%% for pretty printing and a nice hypersummary also set:
\Plainauthor{Anne Helby Petersen, Claus Thorn Ekstr\o m} %% comma-separated
\Plaintitle{{cleanR}: maid for cleaning datasets in R} %% without formatting
\Shorttitle{\pkg{cleanR}: maid for cleaning datasets in R} %% a short title (if necessary)

@@

%% The address of (at least) one author should be given
%% in the following format:
\Address{
  Claus Thorn Ekstr\o m\\
  Biostatistics, Department of Public Health\\
  University of Copenhagen\\
  Denmark\\
  E-mail: \email{ekstrom@sund.ku.dk}\\
  URL: \url{http://staff.pubhealth.ku.dk/~ekstrom/}
}
%% It is also possible to add a telephone and fax number
%% before the e-mail in the following format:
%% Telephone: +43/512/507-7103
%% Fax: +43/512/507-2851

@@

The manusccript is organized as follows. Section \ref{sec:example1}
presents a worked example and tutorial on how to use the \pkg{cleanR}
package to create a summary of potential errors. Section
\ref{sec:internals} presents the steps that comprise the creation of
the automated data cleaning that is part of the \code{clean} function,
while the \ref{sec:extending} Section explains how the set of checks
and graphical visualisations that are part of the cleaning suite are
extended by custom, used-written additions. Finally, plans for
extending the package are described in Section \ref{sec:conclusion}.

@@

In \pkg{cleanR} the \code{clean} function is the primary workhorse and it
should be the primary entry point for data cleaning.
